Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-09-21 tex/sup/supplementary_information.tex
数据介绍大纲

\section*{Methods S2. Detailed information on dataset and processing}
Since the Yellow River Basin consists of ten provincial areas, the above division can also maintain broad consistency with administrative divisions.
Add a materials' subsection if you need to.

>>>>

\section*{Methods S2. Detailed information on dataset and processing}

Multiple datasets were used in this study. 
\subsection*{Statistical datasets}
The 2nd National Water Resources Assessment Program.

\subsection*{Hydrological datasets}

\subsection*{Political datasets}

\section{Methods S4.  Detailed information on data processing}
